---
title: 'survival_model.rmd'
author: "fernandezr5"
output: 
  html_document:
          toc: true  
          toc_depth: 3
          number_sections: false
          theme: cosmo
          toc_float: true
---
  
```{r,echo=FALSE,message=FALSE,warning=FALSE,include=FALSE}
require("adapr") 
require("methods") 
require("knitr") 
require('kableExtra')
```

# Covariate Table
♠
```{r echo=FALSE, fig.align='center'}
cov_tab1
```

# Variable Comparisons

## Event Variable Comparison

```{r echo=FALSE}
sa_allc_var_comparisons
```

## Time of Death Comparison

```{r echo=FALSE}
time_death_table
```

# Event Summaries

```{r echo=FALSE, fig.align='center'}
event_summary1
```

<br>

  ```{r echo=FALSE, fig.align='center'}
event_summary2
```

# 15 Year Mortality

```{r echo=FALSE}
kable(mortality_15yr) %>%
  kable_styling(full_width = T)
```

# Survival Models

## Adenine Adjusted Model (ESRD)

```{r echo=FALSE, fig.align='center'}
model_newvar
```

## Fully Adjusted (Unweighted)

```{r echo=FALSE, fig.align='center'}
model5
```

# Combined Concordance

```{r echo=FALSE}
combined_c_index_table %>%
  gt(rowname_col = 'model')
```

# Subset Models Adenine In

```{r echo=FALSE, fig.align='center'}
forest_plots
```

## Sex

```{r echo=FALSE, fig.align='center'}
all_subset_results$adenine_in$subset_summaries$sex %>%
  tbl_merge(tab_spanner = c('Male', 'Female'))
```

## ACR Groups

```{r echo=FALSE}
all_subset_results$adenine_in$subset_summaries$acr_group %>%
  tbl_merge(tab_spanner = levels(subset_dataset$acr_group))
```

## Model Results

```{r echo=FALSE, fig.align='center'}
tertile_km_hazard
```

```{r echo=FALSE, fig.align='center'}
surv_tbl_stack
```

## GFIF Table

```{r echo=FALSE}
vif_tab
```

# Covariate Balance Evaluation

## Fully Adjusted

```{r echo=FALSE}
propensity_weight_list$cbpsdata2$balance_df %>%
  gt(rowname_col = 'Variable')
```

## ACR Excluded

```{r echo=FALSE}
propensity_weight_list$cbpsdata3$balance_df %>%
  gt(rowname_col = 'Variable')
```

# Mixed Model

```{r echo=FALSE}
mixed_model_coefs
```

```{r echo=FALSE, fig.align='center'}
effects_plot
```

# Visualization

## Cumulative incidence

```{r echo=FALSE, fig.align='center', warning = F, message=F}
tertile_km_singapore$plot
```

## Effects plot 95% CI

```{r echo=FALSE, fig.align='center'}
effects_plot_singapore1
```

## Effects plot SE

```{r echo=FALSE, fig.align='center'}
effects_plot_singapore2
```
